---
title: "Param_Scan_Results"
author: "Ben Barnhart"
date: "4/20/2021"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
library(fOptions)
library(pracma)
library(NlcOptim)
library(openxlsx)
#library(deSolve)
library(sensitivity)
library(parallel)
library(ggplot2)
library(dplyr)
library(colorspace)
library(reshape2)
library(Matrix)
library(grid)
library(gplots)
rm(list = ls())


opts_chunk$set(root.dir = "~/")

```

Read in initial data
```{r}
comb_res_ults <- readRDS("KCD_Par_ParScan_LLonly.RDS")
names(comb_res_ults) <- c("11171", "11172", "11173", "11174", "A11", "A12", "A13", "A14", "A15", "A16", "A41", "A42", "A43", "A44", "A45", "A46", "BCH27", "BCH28", "BCH29", "BCHF30", "BCHF31", "BUS21", "BUS22", "BUS23", "BUS24")

all_dat <- read.csv("SupplementaryFile3_unzipped/Auxilliary_Code_and_data/All_Rat_Data_final_06_01_2021.csv")

animal_list <- c("11171", "11172", "11173", "11174", "A11", "A12", "A13", "A14", "A15", "A16", "A41", "A42", "A43", "A44", "A45", "A46", "BCH27", "BCH28", "BCH29", "BCHF30", "BCHF31", "BUS21", "BUS22", "BUS23", "BUS24")
```

Reformat data into M-value specific and Kcd-specific lists
```{r}
MLLs <- matrix(nrow = 30, ncol = 100, dimnames = list(1:30, 1:100))
CdLLs <- matrix(nrow = 30, ncol = 100, dimnames = list(1:30, 1:100))
for (i in 1:length(comb_res_ults)) {
  dtemp <- comb_res_ults[[i]]
  if (is.matrix(dtemp)){
    
    MLLs[i,] <- dtemp[,"Kcd_0.1"]
    
    
    colnames(MLLs) <- rownames(dtemp)
    rownames(MLLs)[i] <- animal_list[i]
    CdLLs[i,] <- dtemp["M_20.91",]
    rownames(CdLLs)[i] <- animal_list[i]
    colnames(CdLLs) <- colnames(dtemp)
    
    # uname <- paste(c("CombD_", animal_list[i]), collapse = "")
    # assign(uname, comb_res_ults[[i]], envir = .GlobalEnv)
  } else {
    next
  }

}
```

Set up meta data for help with plotting.
```{r}
annotdf <- unique(all_dat[,c(1,3,4)], fromLast = F)
annotdf$Diet <- factor(all_dat$Diet, levels = c("Chow", "Carbohydrate", "Ethanol"))
annotdf$Animal <- all_dat$Animal[match(all_dat$Sample_Code, annotdf$Sample_Code)]
rownames(annotdf) <- c()
annotdf <- annotdf[order(annotdf$Diet, annotdf$Sex),]


MLLs <- MLLs[match(annotdf$Animal, rownames(MLLs)),]
CdLLs <- CdLLs[match(annotdf$Animal, rownames(CdLLs)),]


```

Figure S4A
```{r}
rgw_pal <- colorspace::sequential_hcl(n = 300, h1 = 140, h2 = 80, c1 = 50, cmax = NA, c2 = 10, l1 = 40, l2 = 97, p1 = 0.7, p2 = 1.8, rev = TRUE)

eee <- pheatmap::pheatmap(na.omit(MLLs), cluster_cols = F, 
                   cluster_rows = T, 
                   scale = "row", 
                   color = rgw_pal, 
                   labels_col = c("5","","","", "---------------->", "","","", "30"), 
                   angle_col = 0, 
                   main = "Metabolic load vs LogLikelihood of Residuals, PHx Liver Regeneration Model",
                   #legend_breaks = c(2,1,0,-1,2)
                   #, annotation_row = diet_an
                   )

annotdf$SexFonts <- ifelse(annotdf$Sex == "Female", "plain", "bold.italic")
annotdf$DietColors <- ifelse(annotdf$Diet == "Ethanol", "red", "blue")
annotdf$DietColors[which(annotdf$Diet == "Chow")] <- "green"

cols = annotdf$DietColors[match(eee$gtable$grobs[[5]]$label, annotdf$Animal)] 
fots = annotdf$SexFonts[match(eee$gtable$grobs[[5]]$label, annotdf$Animal)] 

eee$gtable$grobs[[5]]$gp = gpar(col = cols, fontsize = 10, fontface = fots)
print(eee)


```

Figure S4B
```{r}
fff <- pheatmap::pheatmap(na.omit(CdLLs), cluster_cols = F, 
                   cluster_rows = T, 
                   scale = "row", 
                   color = rgw_pal, 
                   labels_col = c("0.01","","","", "---------------->", "","","", "1"), 
                   angle_col = 0, 
                   #legend_breaks = c(2,1,0,-1,2),
                   main = "K Cell Death vs LogLikelihood of Residuals, PHx Liver Regeneration Model")

cols = annotdf$DietColors[match(fff$gtable$grobs[[5]]$label, annotdf$Animal)] 
fots = annotdf$SexFonts[match(fff$gtable$grobs[[5]]$label, annotdf$Animal)]  

fff$gtable$grobs[[5]]$gp = gpar(col = cols, fontsize = 10, fontface = fots)
print(fff)

```

Get best-fit values for all animals: Needed to make Figure S3 in Plot_Physiological_Data.RMD.
Make sure to uncomment the last line in order to save the .RDS file
```{r}
maxs_M_LL <- matrix(unlist(strsplit( names(unlist(apply(MLLs,1,which.max))), split = "_" )), ncol = nrow(MLLs))
ttt <- unlist(strsplit(as.character(maxs_M_LL[1,]), split = ".M"))
maxs_M_LL[1,] <- ttt
maxs_M_LL <- t(maxs_M_LL)
colnames(maxs_M_LL) <- c("Animal", "M")

maxs_CD_LL <- matrix(unlist(strsplit( names(unlist(apply(CdLLs,1,which.max))), split = "_" )), ncol = nrow(CdLLs))
ttt <- unlist(strsplit(as.character(maxs_CD_LL[1,]), split = ".Kcd"))
maxs_CD_LL[1,] <- ttt
maxs_CD_LL <- t(maxs_CD_LL)
colnames(maxs_CD_LL) <- c("Animal", "Kcd")

maxs_all <- merge(maxs_M_LL, maxs_CD_LL, by = "Animal")
maxs_all <- unique(maxs_all)

#saveRDS(maxs_all, file = "Best_fit_M_Kcd_all_animals.RDS")
```


Figure S4C-F
```{r}
rgw_pal <- colorspace::sequential_hcl(n = 299, h1 = 140, h2 = 80, c1 = 50, cmax = NA, c2 = 10, l1 = 40, l2 = 97, p1 = 0.7, p2 = 1.8, rev = TRUE)

for (i in 1:length(comb_res_ults)) {
  dtemp <- comb_res_ults[[i]]
  if (is.matrix(dtemp)){
    dtemp <- t(dtemp)
    dtemp <- flipdim(dtemp, dim = 1)
    
    pcolors = rgw_pal
    pbreaks = c(seq(from = -150, to = 10, length.out = 100))
    # lbr = c("Kcd = 1.0", rep("", 18), "Kcd = 0.8", rep("", 19), "Kcd = 0.6", rep("", 18), "Kcd = 0.4", rep("", 19), "Kcd = 0.2", rep("", 19), "Kcd = 0.01")
    # lbc = c("M = 30", rep("", 18), "M = 25", rep("", 19), "M = 20", rep("", 18), "M = 15", rep("", 19), "M = 10", rep("", 19), "M = 5")
    lbr = c()
    lbc = c()
    
    
    # phm <- pheatmap::pheatmap(na.omit(dtemp), 
    #                  cluster_cols = F, 
    #                  cluster_rows = F, 
    #                  show_rownames = T,
    #                  scale = "none", 
    #                  color = pcolors, 
    #                  labels_col = c("5","","","", "---------------->", "","","", "30"), 
    #                  angle_col = 0, 
    #                  legend_breaks = pbreaks,
    #                  main = paste("Metabolic Load vs K Cell Death LogLikelihood of Residuals, ", animal_list[i]))
    
    phm <- heatmap.2(na.omit(dtemp), dendrogram = 'none',
                     scale = "none", trace = 'none', symkey = TRUE, symbreaks = TRUE,
                     col = pcolors, 
                     breaks = pbreaks, 
                     Rowv = F,
                     ALSE, Colv = FALSE, density.info = 'none',
                     labRow = lbr, labCol = lbc, main = paste(animal_list[i]))
    
    
    phm
  } else {
    next
  }
}


# pheatmap::pheatmap(na.omit(CombD_11171), cluster_cols = F, cluster_rows = F, scale = "row", color = diverge_hsv(n = 100), labels_col = c("0.01","","","", "---------------->", "","","", "1"), angle_col = 0, main = "K Cell Death vs LogLikelihood of Residuals, PHx Liver Regeneration Model")
```


Import volume data from scans
```{r}
#vol_dat <- readRDS("Volume_Data_weighted_range.RDS")
vol_dat <- readRDS("Volume_Data_unweighted_range.RDS")

use_these <- vol_dat
use_these <- t(use_these)
use_these <- flipdim(use_these, dim = 1)
#pheatmap::pheatmap(na.omit(use_these), cluster_cols = F, 
                   # cluster_rows = F, 
                   # scale = "none", 
                   # color = diverge_hsv(n = 100), 
                   # labels_col = c("5","","","", "---------------->", "","","", "30"), 
                   # angle_col = 0, 
                   # main = "K Cell Death vs LogLikelihood of Residuals, PHx Liver Regeneration Model")


```


Volume at 1 week parameter scan for each animal, highlighting top 5% best fit data, Figure S5
```{r}
for (i in 1:length(comb_res_ults)) {
  #browser()
  dtemp <- comb_res_ults[[i]]
  if (is.matrix(dtemp)) {
    dtemp <- reshape2::melt(dtemp)
    colnames(dtemp) <- c("MetL", "Kap", "LogLik")
    M_temp <- unlist(strsplit(as.character(dtemp$MetL), split = "_"))
    M_temp <- M_temp[c(FALSE, TRUE)]
    cd_temp <- unlist(strsplit(as.character(dtemp$Kap), split = "_"))
    cd_temp <- cd_temp[c(FALSE, TRUE)]
    dtemp$MetL <- as.numeric(M_temp); dtemp$Kap <- as.numeric(cd_temp)
    
    relvols <- reshape2::melt(use_these)
    M_temp <- unlist(strsplit(as.character(relvols$Var2), split = "_"))
    M_temp <- M_temp[c(FALSE, TRUE)]
    relvols$Var2 <- as.numeric(M_temp)
    cd_temp <- unlist(strsplit(as.character(relvols$Var1), split = "Par30"))
    cd_temp <- cd_temp[c(FALSE, TRUE)]
    relvols$Var1 <- as.numeric(cd_temp)
    
    colnames(relvols) <- c("Kap", "MetL", "Vol_1week")
    relvols$three_color <- c(rep(NA, nrow(relvols)))
    relvols$three_color[which(relvols$Vol_1week < 0.4)] <- "Failure"
    relvols$three_color[which(relvols$Vol_1week >= 0.4 & relvols$Vol_1week < 0.85)] <- "Suppressed"
    relvols$three_color[which(relvols$Vol_1week >= 0.85)] <- "Healthy"
    mtind <- apply(dtemp, 1, function(x){ unlist(which(relvols$Kap == x[2] & relvols$MetL == x[1])) })
    relvols$LogLike[mtind] <- dtemp$LogLik
    
    LLT <- max(dtemp$LogLik) - ((max(dtemp$LogLik) -  min(dtemp$LogLik) )/ 20)
    relvols$LogLikeThresh <- c(rep(NA, nrow(relvols)))
    relvols$LogLikeThresh[which(relvols$LogLike > LLT)] <- 1
    relvols$LogLikeThresh[which(relvols$LogLike <= LLT)] <- 0
    
    aname <- animal_list[i] 
    adiet <- annotdf$Diet[which(annotdf$Animal == aname)]
    asex <- annotdf$Sex[which(annotdf$Animal == aname)]
    
    # vxf <- ggplot(data = NULL, aes(x = MetL, y = Kap)) + theme_classic() + ggtitle(paste(aname, adiet, asex, sep = ", ")) + 
    #   xlab("Metabolic Load (artificial value)") + ylab("K of Apoptosis (artificial value)") +
    #   geom_jitter(data = dtemp, aes(color = LogLik)) +  scale_color_gradient2(name = "Log Likelihood",low = "blue", mid = "white", high = "red") +
    #   scale_x_continuous(breaks = c(5,10,15,20,25,30)) + 
    #   scale_y_continuous(breaks = c(0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1))
    
    if (i == 1){
      vxf <- ggplot(data = NULL, aes(x = MetL, y = Kap)) + theme_classic() + ggtitle(paste(aname, adiet, asex, sep = ", ")) +
      xlab("Metabolic Load (a.u.)") + ylab("K of Apoptosis (a.u.)") +
      geom_jitter(data = relvols, aes(color = three_color)) +  scale_color_discrete(name = "Rel. Volume at 1 week") + 
      scale_x_continuous(breaks = c(5,10,15,20,25,30)) +
      scale_y_continuous(breaks = c(0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1))
      print(vxf)
    }
    
    
    # vxx <- ggplot(data = NULL, aes(x = MetL, y = Kap)) + theme_classic() + ggtitle(paste(aname, adiet, asex, sep = ", ")) +
    #   xlab("Metabolic Load (artificial value)") + ylab("K of Apoptosis (artificial value)") +
    #   geom_jitter(data = dtemp, aes(color = LogLik)) +  scale_color_gradient2(name = "Log Likelihood",low = "blue", mid = "white", high = "red") +
    #   scale_x_continuous(breaks = c(5,10,15,20,25,30)) +
    #   scale_y_continuous(breaks = c(0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1)) +
    #   geom_jitter(data = relvols, aes(alpha = Volalpha)) 
    
    vxx <- ggplot(data = NULL, aes(x = MetL, y = Kap)) + theme_classic() + ggtitle(paste(aname, adiet, asex, sep = ", ")) +
      xlab("Metabolic Load (a.u.)") + ylab("K of Apoptosis (a.u.)") +
      geom_jitter(data = relvols, aes(color = three_color, alpha = (LogLikeThresh))) +  scale_color_discrete(name = "Rel. Volume at 1 week") + 
      scale_x_continuous(breaks = c(5,10,15,20,25,30)) +
      scale_y_continuous(breaks = c(0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1))
    print(vxx)
    
    
    
  } else {
  }
}
```

