---
title: "Multivariate_US_Analysis"
author: "Ben_Barnhart"
date: "7/14/2020"
output: html_document
---

```{r}
rm(list = ls())


library(knitr)
library(ggplot2)
library(dplyr)
library(patchwork)
library(Rcpp)
library(lme4)
library(MARSS)
library(openxlsx)
library(nlme)
library(ggpmisc)
library(ggpubr)
#library(edge)
library(sciplot)
library(lsr)
library(tidyverse)
library(ggpubr)
library(rstatix)
library(emmeans)

opts_chunk$set(root.dir = "M:/Dropbox (SBG)/Benjamin-Barnhart/Ultrasound_CT_imagingData/")

#opts_chunk$set(root.dir = "C:/Users/benja/Dropbox (SBG)/Benjamin-Barnhart/Ultrasound_CT_imagingData")
```



Read in data + calculate group averages. 
```{r}
#all_dat <- read.xlsx("All rats data 02172020.xlsx", na.strings = "", colNames = TRUE, rowNames = TRUE, sheet = "For_R_Import")
all_dat <- read.csv("M:/Dropbox (SBG)/Benjamin-Barnhart/Ultrasound_CT_imagingData/All_Rat_Data_final_06_01_2021.csv", row.names = 1)

all_dat$PV_raw <- (pi * (all_dat$PV_diameter / 2)^2) * all_dat$PV_velocity


m1 <- all_dat[,5:13]
m1 <- apply(all_dat[,5:13], 2, as.numeric)
exp_group <- factor(paste(all_dat$Sex, all_dat$Diet, all_dat$Time, sep = "_"))

ave_dat <- aggregate(m1, by = list(exp_group), FUN = "mean", na.action = NULL, na.rm = TRUE)
sd_dat <- aggregate(m1, by = list(exp_group), FUN = "sd", na.rm = TRUE)

ave_dat_an <- matrix(unlist(strsplit(x = as.character(ave_dat$Group.1), split = "_", )), nrow = nrow(ave_dat), byrow = TRUE)
colnames(ave_dat_an) <- c("Sex", "Diet", "Time")

ave_dat <- cbind(ave_dat_an, ave_dat)
sd_dat <- cbind(ave_dat_an, sd_dat)
ave_dat <- ave_dat[,-4]
sd_dat <- sd_dat[,-4]
# rm_col <- which(names(ave_dat) == "Animal"| names(ave_dat) == "Time"| names(ave_dat) == "Sex" | names(ave_dat) == "Diet")
# ave_dat <- ave_dat[,-rm_col]
# sw_col <- which(names(ave_dat) == "Group.1"| names(ave_dat) == "Group.2"| names(ave_dat) == "Group.3")
# names(ave_dat)[sw_col] <- c("Time", "Sex", "Diet")
# 
ave_datm <- ave_dat[which(ave_dat[,"Sex"] == "Male"),]
ave_datf <- ave_dat[which(ave_dat[,"Sex"] == "Female"),]
sd_datm <- sd_dat[which(sd_dat[,"Sex"] == "Male"),]
sd_datf <- sd_dat[which(sd_dat[,"Sex"] == "Female"),]

# all_dat_full <- na.omit(all_dat)
# 
# all_dat_vol_only <- all_dat[,1:6]
# all_dat_abridge <- na.omit(all_dat_vol_only)


```


Data preparation for anova. Removing all Chow fed animals, converting all grouping variables into factors. 
```{r}
model_dat <- all_dat
model_dat$Time[which(model_dat$Time == -24)] <- "a_Presurgery"
model_dat$Time[which(model_dat$Time == 0.3)] <- "b_20_minutes"
model_dat$Time[which(model_dat$Time == 10)] <- "c_10_hours"
model_dat$Time[which(model_dat$Time == 24)] <- "d_24_hours"
model_dat$Time[which(model_dat$Time == 48)] <- "e_48_hours"
model_dat$Time[which(model_dat$Time == 72)] <- "f_3_days"
model_dat$Time[which(model_dat$Time == 96)] <- "g_4_days"
model_dat$Time[which(model_dat$Time == 168)] <- "h_7_days"
model_dat$Time[which(model_dat$Time == 336)] <- "i_2_weeks"

model_dat$Time <- factor(model_dat$Time, ordered = TRUE, 
                         levels = c("a_Presurgery", "b_20_minutes", "c_10_hours", "d_24_hours", "e_48_hours", "f_3_days", "g_4_days", "h_7_days", "i_2_weeks"))



model_dat$Animal <- factor(model_dat$Animal)
#model_dat$Diet <- factor(model_dat$Diet)
#model_dat$Time <- as.character(model_dat$Time)

#model_dat2 <- model_dat[which(model_dat$Time != "-24"),]
model_dat2 <- model_dat[which(model_dat$Diet != "Chow"),]
model_dat2$Diet <- factor(model_dat2$Diet, ordered = FALSE, levels = c("Carbohydrate", "Ethanol"))
model_dat2$Sex <- factor(model_dat2$Sex)
```


Main Statistical Tests:
Shown for Portal flow ("PV_flow"). Replace "PV_flow" throughout this code chunk with relevant column name in model_dat2 in order to get results for other measures. 
```{r}


modelo  <- lm(PV_flow ~ Sex*Diet*Time, data = model_dat2)

modelo.aov <- anova_test(data = model_dat2, formula = PV_flow ~ Sex*Diet*Time)
get_anova_table(modelo.aov)

pwc1 <- model_dat2 %>%
  group_by(Sex, Diet) %>%
  emmeans_test(PV_flow ~ Time, p.adjust.method = "bonferroni", model = modelo) #%>%
  #select(-df, -p) # Remove details
pwc2 <- model_dat2 %>%
  group_by(Sex, Time) %>%
  emmeans_test(PV_flow ~ Diet, p.adjust.method = "bonferroni", model = modelo) #%>%
  #select(-df, -p) # Remove details
pwc3 <- model_dat2 %>%
  group_by(Time, Diet) %>%
  emmeans_test(PV_flow ~ Sex, p.adjust.method = "bonferroni", model = modelo ) #%>%
  #select(-df, -p) # Remove details

# pwc4 <- model_dat2 %>%
#   group_by(Time) %>%
#   emmeans_test(Volume_Norm ~ Sex*Diet, p.adjust.method = "bonferroni") %>%
#   select(-df, -statistic, -p) # Remove details

# Show comparison results for male ethanol
# pwc1 %>% filter(Sex == "Male", Diet == "Ethanol")
# 
me_means <- get_emmeans(pwc1) %>% filter(Sex == "Male", Diet == "Ethanol")
# mc_means <- get_emmeans(pwc) %>% filter(Sex == "Male", Diet == "Carbohydrate")
# fe_means <- get_emmeans(pwc) %>% filter(Sex == "Female", Diet == "Ethanol")
# fc_means <- get_emmeans(pwc) %>% filter(Sex == "Female", Diet == "Carbohydrate")
```

Use Levene's Test for homogeneity of variance. 
```{r}
model_dat2 %>%
  group_by(Time) %>%
  levene_test(PV_flow ~ Sex*Diet)
```


Checking for correlations between M/Kcd and initial US measurements (Figure S3)
```{r}
#maxs_all <- readRDS("Best_fit_M_Kcd_all_animals.RDS")
maxs_all <- readRDS("Best_fit_M_Kcd_all_animals_weighted.RDS")

check_dat <- all_dat[which(all_dat$Time == -24),]
check_dat <- merge(check_dat, maxs_all, by = "Animal")
check_dat$M <- as.numeric(check_dat$M)
check_dat$Kcd <- as.numeric(check_dat$Kcd)

for (i in c(5,7,8,9,10,11)) {
  var_name <- colnames(check_dat)[i]
  yax <- range(check_dat$M, na.rm = TRUE)
  yax[1] <- yax[1] - 5; yax[2] <- yax[2] + 5

  xax <- range(check_dat[,i], na.rm = TRUE)
  xax[1] <- xax[1] - (xax[2]/10); xax[2] <- xax[2] + (xax[2]/10)
  
  lx <- ggplot(data = check_dat, aes(x = check_dat[,i], y = `M`)) +
    theme(axis.text = element_text(size = 15), axis.title = element_text(size = 15), legend.position = "right") +
    geom_point(aes(shape = Sex, color = Diet, size = 1.5)) + theme_classic() +
    scale_color_manual(values = c( "#0000FF","#008000", "#FF0000")) + #  is green
    # labs(title = "Relationship between liver size and bodyweight") +
    ylab("Metabolic Load") + xlab(paste(var_name)) +
    ylim(yax) + xlim(xax) +
    stat_smooth( method = "lm", formula = y ~ x , size = 1, data = check_dat) +
    stat_cor(label.x.npc = "left", label.y.npc = "top", size = 6) + 
    stat_regline_equation(label.x.npc = "left", label.y.npc = "bottom", size = 6)

  print(lx)
}

for (i in c(5,7,8,9,10,11)) {
  var_name <- colnames(check_dat)[i]
  yax <- range(check_dat$Kcd, na.rm = TRUE)
  yax[1] <- yax[1] - 1; yax[2] <- yax[2] + 1

  xax <- range(check_dat[,i], na.rm = TRUE)
  xax[1] <- xax[1] - (xax[2]/10); xax[2] <- xax[2] + (xax[2]/10)
  
  lxxx <- ggplot(data = check_dat, aes(x = check_dat[,i], y = Kcd)) +
    geom_point(aes(shape = Sex, color = Diet, size = 1.5)) + theme_classic() +
    #theme(axis.text = element_text(size = 15), axis.title = element_text(size = 15)) +
    scale_color_manual(values = c( "#0000FF","#008000", "#FF0000")) + #  is green
    # labs(title = "Relationship between liver size and bodyweight") +
    ylab("Cell Death Constant") + xlab(paste(var_name)) +
    theme(legend.position = "right") +
    ylim(yax) + xlim(xax) +
    stat_smooth( method = "lm", formula = y ~ x , size = 1, data = check_dat) +
    stat_cor(label.x.npc = "left", label.y.npc = "top", size = 6) + 
    stat_regline_equation(label.x.npc = "left", label.y.npc = "bottom", size = 6)

  print(lxxx)
}
```

Normalized Volume Recovery Plot (Figure 2A)
```{r}
yax <- range(all_dat$Volume_Norm, na.rm = TRUE)
yax[1] <- yax[1] - 0.5; yax[2] <- yax[2] + 0.5

dat_1 <- all_dat[which(all_dat$Diet == "Carbohydrate" | all_dat$Diet == "Ethanol"),]
dat_1$Time <- as.character(dat_1$Time)

# dat_1a <- dat_1[which(dat_1$Sex == "Male"),]
# dat_1b <- dat_1[which(dat_1$Sex == "Female"),]


lx <- ggplot(data = dat_1, aes(x = Time, y = Volume_Norm)) + 
  theme_classic() + theme(axis.text = element_text(size = 20), axis.title = element_text(size = 20)) +
  #geom_violin(scale = "area", ) +  
  #geom_dotplot(binaxis = "y", stackdir = "center", position=position_dodge(1), dotsize = 0.5, fill = "white") +
  #geom_split_violin(aes(colour = Diet)) +
  geom_point(aes(colour = Diet), size = 2.5) +
  geom_path(aes(group = Animal), alpha = 0.3) +
  scale_x_discrete(limits = c("-24", "0.3", "10", "24", "48", "72", "96", "168", "336")) +
  scale_color_manual(values = c("#000080", "#FF0000")) + # "#008000", is green
  labs(title = "Liver Volume Recovery") + 
  ylab("Normalized Volume (mm^3) / Bodyweight (g)") + xlab("Hours Post-PHx") + 
  theme(legend.position = "none") + ylim(yax) +
  facet_wrap(~Sex, ncol = 1) #+
  
  #geom_text(size = 2,  vjust = "inward", nudge_x = 0.2)
print(lx)

```


Scatter plot of all data with regression between raw volume and bodyweight (Figure 3B,C)
```{r}
# somePDFpath <- "M:/Dropbox (SBG)/Benjamin-Barnhart/Ultrasound_CT_imagingData/pdf1.pdf"
# pdf(file = somePDFpath)

dat_1 <- all_dat[which(all_dat$Diet != "Chow"), ]
dat_1 <- dat_1[which(dat_1$Time != 96),]

yax <- range(dat_1$Volume_raw, na.rm = TRUE)
yax[1] <- yax[1] - 50; yax[2] <- yax[2] + 50

xax <- range(dat_1$Bodyweight, na.rm = TRUE)
xax[1] <- xax[1] - 50; xax[2] <- xax[2] + 50

dat_2 <- dat_1[which(dat_1$Time != "336"),]
dat_3 <- dat_1[which(dat_1$Time == "-24"),]

lx <- ggplot(data = dat_1, aes(x = Bodyweight, y = Volume_raw)) + 
  theme_classic() + theme(axis.text = element_text(size = 20), axis.title = element_text(size = 20)) +
  geom_point(aes(color = Diet)) + 
  geom_point(data = dat_3, shape = 2, size = 3, aes(x = Bodyweight, y = Volume_raw)) +
  geom_path(aes(group = Animal)) +
  # geom_line() +
  #scale_x_discrete(limits = c("negative", "positive")) +
  scale_color_manual(values = c( "#0000FF", "#FF0000")) + #"#008000"  is green
  # labs(title = "Relationship between liver size and bodyweight") + 
  ylab("Liver Volume (mm^3)") + xlab("Bodyweight (g)") + 
  theme(legend.position = "none") + 
  ylim(yax) +
  stat_smooth( method = "lm", formula = y ~ x , size = 1, data = dat_1) +
  stat_cor(label.x.npc = "left", label.y.npc = "top", size = 10) +
  facet_wrap(~Sex, ncol = 1)
  
  #stat_poly_eq(parse = T, aes(label = ..eq.label..), formula = y ~ x)

print(lx)

mx <- ggplot(data = dat_1, aes(x = Bodyweight, y = Volume_raw)) + 
  theme_classic() + theme(axis.text.y = element_text(size = 20), axis.text.x = element_text(size = 15), axis.title = element_text(size = 20)) +
  geom_point(aes(color = Diet), size = 2) + 
  geom_point(data = dat_3, shape = 2, size = 3, aes(x = Bodyweight, y = Volume_raw)) +
  #geom_path(aes(group = Animal)) +
  # geom_line() +
  #scale_x_discrete(limits = c("negative", "positive")) +
  scale_color_manual(values = c( "#0000FF", "#FF0000")) + #"#008000"  is green
  # labs(title = "Relationship between liver size and bodyweight") + 
  ylab("Liver Volume (mm^3)") + xlab("Bodyweight (g)") + 
  theme(legend.position = "none") + 
  ylim(yax) +
  stat_smooth(aes(group = Time), method = "lm", formula = y ~ x , size = 1, data = dat_2, se = FALSE) +
  stat_cor(label.y = 10500, ) + stat_regline_equation(label.y = 10000) +
  #stat_cor(label.x.npc = "left", label.y.npc = "top") +
  facet_wrap(Sex ~ Time, ncol = 8)

print(mx)
# dev.off()

```

Regression of Volume vs PV_flow, all samples (Figure S1C)
```{r}
yax <- range(all_dat$Volume_Norm, na.rm = TRUE)
yax[1] <- yax[1] - 0.5; yax[2] <- yax[2] + 0.5

xax <- range(all_dat$PV_raw, na.rm = TRUE)
xax[1] <- xax[1] - 0.5; xax[2] <- xax[2] + 0.5

lx <- ggplot(data = all_dat, aes(x = PV_raw, y = Volume_Norm)) + 
  theme_classic() +
  geom_point(aes(shape = Sex, color = Diet)) + 
  # geom_line() +
  #scale_x_discrete(limits = c("negative", "positive")) +
  scale_color_manual(values = c( "#0000FF","#008000", "#FF0000")) + #  is green
  # labs(title = "Relationship between liver size and bodyweight") + 
  ylab("Liver Volume (rel)") + xlab("PV_flow") + 
  theme(legend.position = "right") + 
  ylim(yax) +
  stat_smooth( method = "lm", formula = y ~ x , size = 1, data = all_dat) +
  stat_cor(label.x.npc = "left", label.y.npc = "top")
  
  #stat_poly_eq(parse = T, aes(label = ..eq.label..), formula = y ~ x)

print(lx)

```

PV flow vs Stiffness (Figure S2B)
```{r}
yax <- range(all_dat$Stiffness, na.rm = TRUE)
yax[1] <- yax[1] - 0.5; yax[2] <- yax[2] + 0.5

xax <- range(all_dat$PV_flow, na.rm = TRUE)
xax[1] <- xax[1] - 0.5; xax[2] <- xax[2] + 0.5

lx <- ggplot(data = all_dat, aes(x = PV_flow, y = Stiffness)) + 
  theme_classic() +
  geom_point(aes(shape = Sex, color = Diet)) + 
  # geom_line() +
  #scale_x_discrete(limits = c("negative", "positive")) +
  scale_color_manual(values = c( "#0000FF","#008000", "#FF0000")) + #  is green
  # labs(title = "Relationship between liver size and bodyweight") + 
  ylab("Liver Stiffness (m/s)") + xlab("Portal Flow (cubic mm / s)") + 
  theme(legend.position = "right") + 
  ylim(yax) +
  stat_smooth(method = "lm", formula = y ~ x , size = 1, data = all_dat) +
  stat_cor(label.x.npc = "left", label.y.npc = "top")
  
  #stat_poly_eq(parse = T, aes(label = ..eq.label..), formula = y ~ x)

print(lx)
```

Normalized Volume at 1 week vs Portal Flow at 10 hrs (Figure S1A)
```{r}
dat_1w <- all_dat[which(all_dat$Time == 168), c(1:4,6)] #All Volume data at 1 week
dat_1d <- all_dat[which(all_dat$Time == 10), c(1:4, 8)] #All portal flow data at 10 hours post-PHx
#names(dat_1d) <- c("Animal",  "Time1",    "Sex",     "Diet",    "PV_flow")
dat_merg <- merge(dat_1w, dat_1d, by = c("Animal", "Sex", "Diet"))


yax <- range(dat_merg$Volume_Norm, na.rm = TRUE)
yax[1] <- yax[1] - 0.5; yax[2] <- yax[2] + 0.5

xax <- range(dat_merg$PV_flow, na.rm = TRUE)
xax[1] <- xax[1] - 0.5; xax[2] <- xax[2] + 0.5

lx <- ggplot(data = dat_merg, aes(x = PV_flow, y = Volume_Norm)) + 
  theme_classic() +
  geom_point(aes(shape = Sex, color = Diet)) + 
  # geom_line() +
  #scale_x_discrete(limits = c("negative", "positive")) +
  scale_color_manual(values = c( "#0000FF","#008000", "#FF0000")) + #  is green
  # labs(title = "Relationship between liver size and bodyweight") + 
  ylab("Relative Volume (1 week time point)") + xlab("PV_flow (10 hr time point)") + 
  theme(legend.position = "right") + 
  ylim(yax) +
  stat_smooth(method = "lm", formula = y ~ x , size = 1, data = dat_merg) +
  stat_cor(label.x.npc = "left", label.y.npc = "top")
  
  #stat_poly_eq(parse = T, aes(label = ..eq.label..), formula = y ~ x)

print(lx)
```

Normalized Volume at 1 week vs Portal Flow at 24 hrs (Figure S1A)
```{r}
dat_1w <- all_dat[which(all_dat$Time == 168), c(1:4,6)] #All Volume data at 1 week
dat_1d <- all_dat[which(all_dat$Time == 24), c(1:4, 8)] #All portal flow data at 10 hours post-PHx
#names(dat_1d) <- c("Animal",  "Time1",    "Sex",     "Diet",    "PV_flow")
dat_merg <- merge(dat_1w, dat_1d, by = c("Animal", "Sex", "Diet"))


yax <- range(dat_merg$Volume_Norm, na.rm = TRUE)
yax[1] <- yax[1] - 0.5; yax[2] <- yax[2] + 0.5

xax <- range(dat_merg$PV_flow, na.rm = TRUE)
xax[1] <- xax[1] - 0.5; xax[2] <- xax[2] + 0.5

lx <- ggplot(data = dat_merg, aes(x = PV_flow, y = Volume_Norm)) + 
  theme_classic() +
  geom_point(aes(shape = Sex, color = Diet)) + 
  # geom_line() +
  #scale_x_discrete(limits = c("negative", "positive")) +
  scale_color_manual(values = c( "#0000FF","#008000", "#FF0000")) + #  is green
  # labs(title = "Relationship between liver size and bodyweight") + 
  ylab("Relative Volume (1 week time point)") + xlab("PV_flow (24 hr time point)") + 
  theme(legend.position = "right") + 
  ylim(yax) +
  stat_smooth(method = "lm", formula = y ~ x , size = 1, data = dat_merg) +
  stat_cor(label.x.npc = "left", label.y.npc = "top")
  
  #stat_poly_eq(parse = T, aes(label = ..eq.label..), formula = y ~ x)

print(lx)
```


PV_flow Data shown as timeseries with trendline (Figure 4A, D)
```{r}
yax <- range(all_dat$PV_flow, na.rm = TRUE)
yax[1] <- yax[1] - 0.5; yax[2] <- yax[2] + 0.1

dat_1 <- all_dat[which(all_dat$Diet == "Ethanol" | all_dat$Diet == "Carbohydrate"),]
dat_fit <- dat_1[which(dat_1$Time != -24),]

ylabb <- expression(paste("mL/min", cm^3))

lx <- ggplot(data = dat_1, aes(x = Time, y = PV_flow, colour = Diet)) + 
  theme_classic() + theme(axis.text = element_text(size = 20), axis.title = element_text(size = 20)) +
  stat_smooth(aes(y = PV_flow), method = "lm", formula = y ~ x + I(x^2)+ I(x^3), size = 1.25, data = dat_1) +
  #stat_smooth(aes(y = PV_flow), method = "lm", formula = y ~ x + I(x^2)+ I(x^3), size = 1.25, data = dat_1) +
  geom_point(alpha = 1, size = 2) + 
  geom_path(aes(group = Animal), size = 0.5, alpha = 0.5) +
  #scale_x_discrete(limits = c("negative", "positive")) +
  scale_color_manual(values = c("#0000FF", "#FF0000")) + # "#008000", is green
  labs(title = "PV_flow after PHx in Male Rats") + 
  ylab(ylabb) + xlab("Hours Post-PHx") + 
  theme(legend.position = "none") + 
  ylim(yax) + xlim(-50, 200) +
  facet_wrap(~Sex, ncol = 1)
  #geom_text(size = 2,  vjust = "inward", nudge_x = 0.2)
print(lx)

px <- ggplot(data = dat_1, aes(x = Time, y = PV_flow, colour = Sex)) + 
  theme_classic() + theme(axis.text = element_text(size = 20), axis.title = element_text(size = 20)) +
  stat_smooth(aes(y = PV_flow), method = "lm", formula = y ~ x + I(x^2)+ I(x^3), size = 1.25, data = dat_1) +
  #stat_smooth(aes(y = PV_flow), method = "lm", formula = y ~ x + I(x^2)+ I(x^3), size = 1.25, data = dat_1) +
  geom_point(alpha = 1, size = 2) + 
  geom_path(aes(group = Animal), size = 0.5, alpha = 0.5) +
  #scale_x_discrete(limits = c("negative", "positive")) +
  scale_color_manual(values = c("darkorange", "purple")) + # "#008000", is green
  labs(title = "Portal Flow Rate after PHx in Male Rats") + 
  ylab(ylabb) + xlab("Hours Post-PHx") + 
  theme(legend.position = "none") + 
  ylim(yax) + xlim(-50, 200) +
  facet_wrap(~Diet, ncol = 1)
  #geom_text(size = 2,  vjust = "inward", nudge_x = 0.2)
print(px)

#as.vector(colors())[grep("orange", as.vector(colors()))]

```

HA flow (Figure S2A)
```{r}
yax <- range(all_dat$HA_flow, na.rm = TRUE)
yax[1] <- yax[1] - 0.5; yax[2] <- yax[2] + 0.1

dat_1 <- all_dat[which(all_dat$Diet == "Ethanol" | all_dat$Diet == "Carbohydrate"),]
dat_fit <- dat_1[which(dat_1$Time != -24),]

ylabb <- expression(paste("mL/min", cm^3))

lx <- ggplot(data = dat_1, aes(x = Time, y = HA_flow, colour = Diet)) + 
  theme_classic() + theme(axis.text = element_text(size = 20), axis.title = element_text(size = 20)) +
  stat_smooth(aes(y = PV_flow), method = "lm", formula = y ~ x + I(x^2)+ I(x^3), size = 1.25, data = dat_1) +
  #stat_smooth(aes(y = PV_flow), method = "lm", formula = y ~ x + I(x^2)+ I(x^3), size = 1.25, data = dat_1) +
  geom_point(alpha = 1, size = 2) + 
  geom_path(aes(group = Animal), size = 0.5, alpha = 0.5) +
  #scale_x_discrete(limits = c("negative", "positive")) +
  scale_color_manual(values = c("#0000FF", "#FF0000")) + # "#008000", is green
  labs(title = "HA_flow after PHx in Male Rats") + 
  ylab(ylabb) + xlab("Hours Post-PHx") + 
  theme(legend.position = "none") + 
  ylim(yax) + xlim(-50, 200) +
  facet_wrap(~Sex, ncol = 1)
  #geom_text(size = 2,  vjust = "inward", nudge_x = 0.2)
print(lx)

px <- ggplot(data = dat_1, aes(x = Time, y = HA_flow, colour = Sex)) + 
  theme_classic() + theme(axis.text = element_text(size = 20), axis.title = element_text(size = 20)) +
  stat_smooth(aes(y = PV_flow), method = "lm", formula = y ~ x + I(x^2)+ I(x^3), size = 1.25, data = dat_1) +
  #stat_smooth(aes(y = PV_flow), method = "lm", formula = y ~ x + I(x^2)+ I(x^3), size = 1.25, data = dat_1) +
  geom_point(alpha = 1, size = 2) + 
  geom_path(aes(group = Animal), size = 0.5, alpha = 0.5) +
  #scale_x_discrete(limits = c("negative", "positive")) +
  scale_color_manual(values = c("darkorange", "purple")) + # "#008000", is green
  labs(title = "Hepatic Artery Flow Rate after PHx in Male Rats") + 
  ylab(ylabb) + xlab("Hours Post-PHx") + 
  #theme(legend.position = "none") + 
  ylim(yax) + xlim(-50, 200) +
  facet_wrap(~Diet, ncol = 1)
  #geom_text(size = 2,  vjust = "inward", nudge_x = 0.2)
print(px)
```



Stiffness (Figure 4B, E)
```{r}
yax <- range(all_dat$Stiffness, na.rm = TRUE)
yax[1] <- yax[1] - 0.5; yax[2] <- yax[2] + 0.1

dat_1 <- all_dat[which(all_dat$Diet == "Ethanol" | all_dat$Diet == "Carbohydrate"),]
dat_fit <- dat_1[which(dat_1$Time != -24),]

lx <- ggplot(data = dat_1, aes(x = Time, y = Stiffness, colour = Diet)) + 
  theme_classic() + theme(axis.text = element_text(size = 20), axis.title = element_text(size = 20)) +
  stat_smooth(aes(y = Stiffness), method = "lm", formula = y ~ x + I(x^2)+ I(x^3), size = 1.25, data = dat_1, alpha = 0.5) +
  #stat_smooth(aes(y = Stiffness), method = "lm", formula = y ~ x + I(x^2)+ I(x^3), size = 1.25, data = dat_1, alpha = 0.5) +
  geom_point(alpha = 1, size = 2) + 
  geom_path(aes(group = Animal), size = 0.5, alpha = 0.5) +
  #scale_x_discrete(limits = c("negative", "positive")) +
  scale_color_manual(values = c("#0000FF", "#FF0000")) + # "#008000", is green
  labs(title = "Stiffness Rate after PHx in Male Rats") + 
  ylab("m/s") + xlab("Hours Post-PHx") + 
  theme(legend.position = "none") + 
  ylim(yax) + xlim(-50, 200) +

  facet_wrap(~Sex, ncol = 1)
  #geom_text(size = 2,  vjust = "inward", nudge_x = 0.2)
print(lx)

px <- ggplot(data = dat_1, aes(x = Time, y = Stiffness, colour = Sex)) + 
  theme_classic() + theme(axis.text = element_text(size = 20), axis.title = element_text(size = 20)) +
  stat_smooth(aes(y = Stiffness), method = "lm", formula = y ~ x + I(x^2)+ I(x^3), size = 1.25, data = dat_1) +
  #stat_smooth(aes(y = Stiffness), method = "lm", formula = y ~ x + I(x^2)+ I(x^3), size = 1.25, data = dat_1) +
  geom_point(alpha = 1, size = 2) + 
  geom_path(aes(group = Animal), size = 0.5, alpha = 0.5) +
  #scale_x_discrete(limits = c("negative", "positive")) +
  scale_color_manual(values = c("darkorange", "purple")) + # "#008000", is green
  labs(title = "Stiffness after PHx in Male Rats") + 
  ylab("m/s") + xlab("Hours Post-PHx") + 
  theme(legend.position = "none") + 
  ylim(yax) + xlim(-50, 200) +
  facet_wrap(~Diet, ncol = 1)
  #geom_text(size = 2,  vjust = "inward", nudge_x = 0.2)
print(px)
```

Oxygenations (Figure 4C,F)
```{r}

o2_ex <- expression(paste("Percent ", O^2, "saturation"))

yax <- range(all_dat$Oxygenation, na.rm = TRUE)
yax[1] <- yax[1] - 0.5; yax[2] <- yax[2] + 0.1

dat_1 <- all_dat[which(all_dat$Diet == "Ethanol" | all_dat$Diet == "Carbohydrate"),]
dat_fit <- dat_1[which(dat_1$Time != -24),]


lx <- ggplot(data = dat_1, aes(x = Time, y = Oxygenation, colour = Diet)) + 
  theme_classic() + theme(axis.text = element_text(size = 20), axis.title = element_text(size = 20)) +
  stat_smooth(aes(y = Oxygenation), method = "lm", formula = y ~ x + I(x^2)+ I(x^3), size = 1.25, data = dat_1) +
  stat_cor() + stat_regline_equation(label.y = 50) +
  #stat_smooth(aes(y = Oxygenation), method = "lm", formula = y ~ x + I(x^2)+ I(x^3), size = 1.25, data = dat_1) +
  geom_point(alpha = 1, size = 2) + 
  geom_path(aes(group = Animal), size = 0.5, alpha = 0.5) +
  #scale_x_discrete(limits = c("negative", "positive")) +
  scale_color_manual(values = c("#0000FF", "#FF0000")) + # "#008000", is green
  labs(title = "Tissue Oxygen after PHx in Male Rats") + 
  ylab(o2_ex) + xlab("Hours Post-PHx") + 
  theme(legend.position = "none") + 
  ylim(yax) + xlim(-50, 200) +

  facet_wrap(~Sex, ncol = 1)
  #geom_text(size = 2,  vjust = "inward", nudge_x = 0.2)
print(lx)

px <- ggplot(data = dat_1, aes(x = Time, y = Oxygenation, colour = Sex)) + 
  theme_classic() + theme(axis.text = element_text(size = 20), axis.title = element_text(size = 20)) +
  stat_smooth(aes(y = Oxygenation), method = "lm", formula = y ~ x + I(x^2)+ I(x^3), size = 1.25, data = dat_1) +
  stat_cor() + stat_regline_equation(label.y = 50) +
  #stat_smooth(aes(y = Oxygenation), method = "lm", formula = y ~ x + I(x^2)+ I(x^3), size = 1.25, data = dat_2) +
  geom_point(alpha = 1, size = 2) + 
  geom_path(aes(group = Animal), size = 0.5, alpha = 0.5) +
  #scale_x_discrete(limits = c("negative", "positive")) +
  scale_color_manual(values = c("darkorange", "purple")) + # "#008000", is green
  labs(title = "Tissue Oxygen after PHx in Male Rats") + 
  ylab(o2_ex) + xlab("Hours Post-PHx") + 
  theme(legend.position = "none") + 
  ylim(yax) + xlim(-50, 200) +

  facet_wrap(~Diet, ncol = 1)
  #geom_text(size = 2,  vjust = "inward", nudge_x = 0.2)
print(px)
```


































